Network Structure, Efficiency, and Performance in WikiProjects

### 2018-01-12 paper-content.tex
Update nk figure.
Update tables for nk.

\begin{table*}
\small
\centering
\caption{
Social learning strategies
\label{tab:strat}
}
\bigskip
\begin{tabular}{lccccc}
Name          & Social & Individual & Limited concern & Unknown objective & Single truth \\
\hline
Best+I & Best neighbor   & Global & & & \\
Conf+I & Conformity      & Global & & \Checkmark & \\
Best+LI & Best neighbor  & Local  & \Checkmark & & \\
Conf+LI & Conformity     & Local  & \Checkmark & \Checkmark & \\
LMaj+LI & Local majority & Local  & \Checkmark & \Checkmark & \Checkmark \\
\hline
\end{tabular}
\end{table*}

@@

\begin{table}
\small
\centering
\caption{
Simulated network statistics.
\label{tab:stats}
}
\bigskip
\begin{tabular}{lcc}
Property          & Mean  & Std. Dev. \\
\hline
Mean Degree       & 132.3 & 9.2 \\
Mean Path length  & 1.735 & 0.019 \\
\hline
\end{tabular}
\end{table}

\begin{figure}
\includegraphics[width=3in,height=1.5in]{fig-val-iter.pdf}
\caption{
Mean agent solution value over time, averaged over 100 trials.
The left and right figures show results for agent networks with the probability of
rewiring set to 0 and 1, respectively.
In both, local strategies are less efficient and more performant than non-local.
The consensus strategy is both more efficient and more performant than others,
with its performance increasing with higher rewiring.
\label{fig:val-iter}
}
\end{figure}

\begin{table}
\small
\caption{
Efficiency regression coefficients.
\label{tab:sim-eff}
}
\centering
\bigskip
\begin{tabular}{llc}
Strategy & Std. Coeff. \\
\hline
Best-neighbor       & -0.064 \\
Conformity          & -0.080 \\
Local best-neighbor & -0.086 \\
Local conformity    & \+0.049 \\
Consensus           & -0.0325$^{***}$ \\
\hline
\end{tabular}
\begin{tablenotes}
\item \centering * $p < 0.05$. ** $p < 0.01$. *** $p < 0.001$.
\end{tablenotes}
\end{table}

\begin{table}
\small
\caption{
Performance regression coefficients.
\label{tab:sim-perf}
}
\centering
\bigskip
\begin{tabular}{llc}
Strategy & Std. Coeff. \\
\hline
Best-neighbor       & \+0.084 \\
Conformity          & \+0.130 \\
Local best-neighbor & -0.080 \\
Local conformity    & -0.020 \\
Consensus           & \+2.38$\times{10^{-4\;**}}$ \\
\hline
\end{tabular}
\begin{tablenotes}
\item \centering * $p < 0.05$. ** $p < 0.01$. *** $p < 0.001$.
\end{tablenotes}
\end{table}

\begin{figure*}
\includegraphics[width=6.67in,height=1.33in]{fig-deg-eff.pdf}
\includegraphics[width=6.67in,height=1.33in]{fig-deg-perf.pdf}
\caption{
Efficiency and Performance of social learning strategies vs network degree.
Each point represents a single trial of 300 iterations.
The consensus strategy shows increased performance and decreased efficiency as
degree increases, while other strategies show no degree dependence.
\label{fig:deg-eff-perf}
}
\end{figure*}

@@

The effect of degree on performance and efficiency is shown in Figure \ref{fig:deg-eff-perf} and
Tables \ref{tab:sim-eff} and \ref{tab:sim-perf}.
For both local and non-local versions of the best-neighbor and conformity strategies,
there is no significant effect of degree on performance or efficiency.
As noted above however, the local versions consistently have higher performance and lower efficiency
than their non-local counterparts.
We observe more interesting behavior with the consensus strategy.
Node degree shows a significant negative correlation with degree,
and a small but significant positive correlation with efficiency.
The consensus simulations replicate the efficiency behavior observed in WikiProjects,
but the opposite behavior for performance.
But unlike other strategies, consensus demonstrates that degree distribution can have an
impact on both performance and efficiency.

>>>>

\begin{table*}
\small
\centering
\caption{
Social learning strategies
\label{tab:strat}
}
\bigskip
\begin{tabular}{lccccc}
Name          & Social stage & Individual stage & Limited concern & Unknown objective & Single truth \\
\hline
Best+I & Best neighbor   & Global & & & \\
Conf+I & Conformity      & Global & & \Checkmark & \\
Best+LI & Best neighbor  & Local  & \Checkmark & & \\
Conf+LI & Conformity     & Local  & \Checkmark & \Checkmark & \\
LMaj+LI & Local majority & Local  & \Checkmark & \Checkmark & \Checkmark \\
\hline
\end{tabular}
\end{table*}

@@

\begin{table}
\small
\centering
\caption{
Simulated network statistics.
\label{tab:stats}
}
\bigskip
\begin{tabular}{lcc}
Property          & Mean  & Std. Dev. \\
\hline
Mean Degree       & 116.6 & 1.3 \\
Mean Path length  & 1.766 & 0.0027 \\
\hline
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics[width=2.5in,height=5in]{fig-val-iter.pdf}
\caption{
Mean agent solution value over time, averaged over 100 trials.
The top and bottom figures show results for agent networks with the probability of
rewiring set to 0 and 1, respectively.
In both, local strategies are less efficient than their non-local counterparts.
Local best-neighbor out-performs global,
while local conformity is the worst performer in all cases.
The local majority strategy is both more efficient and more performant than others.
\label{fig:val-iter}
}
\end{figure}

\begin{table}
\small
\caption{
Degree regression coefficients for agent-based models.
\label{tab:sim-perf}
}
\centering
\bigskip
\begin{tabular}{lll}
Strategy & Perf. Std. Coeff. & Eff. Std. Coeff.\\
\hline
Best+I  & -4.2$\times{10^{-5}}$ & \+4.1$\times{10^{-5}}$ \\
Conf+I  & \+2.7$\times{10^{-5}}$ & \+9.4$\times{10^{-5}}$ \\
Best+LI & -9.6$\times{10^{-4\;**}}$ & \+7.7$\times{10^{-5}}$ \\
Conf+LI & -1.5$\times{10^{-3\;***}}$ & \+8.7$\times{10^{-5\;*}}$ \\
LMaj+LI & \+1.2$\times{10^{-4\;**}}$ & -0.038$^{***}$ \\
\hline
\end{tabular}
\begin{tablenotes}
\item \centering * $p < 0.05$. ** $p < 0.01$. *** $p < 0.001$.
\end{tablenotes}
\end{table}

\begin{figure*}
\includegraphics[width=6.67in,height=1.33in]{fig-deg-eff.pdf}
\includegraphics[width=6.67in,height=1.33in]{fig-deg-perf.pdf}
\caption{
Efficiency and Performance of social learning strategies vs. network degree.
Each point represents a single trial of 300 iterations.
The local best-neighbor strategy shows
decreased performance at high degree,
with no significant change in efficiency.
Local conformity shows decreased performance and increased efficiency at high
degree.
Local majority shows the opposite behavior:
increased performance and decreased efficiency at high degree,
with the efficiency showing the largest effect size of all strategies.
\label{fig:deg-eff-perf}
}
\end{figure*}

@@

The effect of degree on performance and efficiency is shown in Figure \ref{fig:deg-eff-perf} and
Table \ref{tab:sim-perf}.
For both local and non-local versions of the best-neighbor and conformity strategies,
there is no significant effect of degree on performance or efficiency.
As noted above however, the local versions consistently have higher performance and lower efficiency
than their non-local counterparts.
We observe more interesting behavior with the consensus strategy.
Node degree shows a significant negative correlation with degree,
and a small but significant positive correlation with efficiency.
The consensus simulations replicate the efficiency behavior observed in WikiProjects,
but the opposite behavior for performance.
But unlike other strategies, consensus demonstrates that degree distribution can have an
impact on both performance and efficiency.
